---
title: 'R Guided Project 01: Creating An Efficient Data Analysis Workflow'
output: html_document
---

```{r}
library(tidyverse)
reviews <- read_csv("book_reviews.csv")
```

This R Markdown file contains analysis of book sales and their reviews.

# Getting Familiar With The Data

A `read_csv` function used above shows some useful information about the imported dataset, but there are also other ways of getting those insights.

```{r}
# How big is the dataset?
dim(reviews)

# What are the column names?
colnames(reviews)

# What is the structure of the dataset?
str(reviews)
```

As we can see, the dataset has 2,000 rows and 4 columns of data.  
Three columns are of character data type, and one of them (called "price") contains numeric values.

```{r}
# What are the unique values in each column?
for (c in colnames(reviews)) {
  print(paste("Unique values in the column:", c))
  print(unique(reviews[[c]]))
  print("")
}
```


# Handling Missing Data

As we could see in the previous step of analysis, the dataset contains some NA values (missing values).  
Let's create a copy of our data which omits all the rows with missing values, and check how many rows we will get.

```{r}
complete_reviews = reviews %>% 
  filter(!is.na(review))

dim(complete_reviews)
```


# Dealing With Inconsistent Labels

One of the previous steps showed that there are inconsistent values in the "state" column of our dataset.  
There are both "New York" and "NY", "California" and "CA", "Texas" and "TX", "Florida" and "FL".  
  
In order to keep these values shorter and more consistent, let's replace the full names with their postal abbreviations.

```{r}
complete_reviews <- complete_reviews %>% 
  mutate(
    state = case_when(
      state == "California" ~ "CA",
      state == "New York" ~ "NY",
      state == "Texas" ~ "TX",
      state == "Florida" ~ "FL",
      TRUE ~ state # ignore cases where it's already postal abbreviation
    )
  )
```


# Transforming The Review Data

The section of code below adds two new columns to the dataset.  
The first of them contains numerical counterparts of descriptive reviews.  
The second one determines whether they are good (high) or not.

```{r}
complete_reviews <- complete_reviews %>% 
  mutate(
    review_num = case_when(
      review == "Poor" ~ 1,
      review == "Fair" ~ 2,
      review == "Good" ~ 3,
      review == "Great" ~ 4,
      review == "Excellent" ~ 5
    ),
    is_high_review = if_else(review_num >= 4, TRUE, FALSE)
  )

# The following line of code shows the first six lines of our tibble.
head(complete_reviews)

# On the other hand, the following command prints its last six lines.
tail(complete_reviews)
```


# Analyzing The Data

In the last step, let's check which book from the dataset was sold the most frequently.

```{r}
complete_reviews %>% 
  group_by(book) %>% 
  summarize(
    purchased = n()
  ) %>% 
  arrange(-purchased)
```

The differences between the titles are not too big, but the most frequently sold book was "Fundamentals of R For Beginners".
